### 2022-02-23 paper/localpsf.tex
updating paper based on advances the last couple months. Work in progress...

\subsection{Idea of the method}
Each impulse response $\impulseresponse_x$ may be interpreted as a scaled probability distribution because of the non-negative impulse response property. Let $\spatialvol(x) := \int_\Omega \impulseresponse_x(y) dy$ denote the scaling factor (the ``volume'' of $\impulseresponse_x$), let $\widehat{\impulseresponse}_x := \impulseresponse_x / \spatialvol(x)$ denote the normalized version of $\impulseresponse_x$, and let $\spatialmean(x)$ and $\spatialcov(x)$ denote the mean and covariance of $\widehat{\impulseresponse}_x$, respectively. In Section \ref{eq:mean_and_covariance_estimation} we will see that it is possible to compute $V(x)$, $\mu(x)$, and $\Sigma(x)$ for all $x \in \Omega$ simultaneously, via a procedure that involves applying $\Aop^T$ to a small number of polynomial functions (three functions if $\gdim=1$, six if $\gdim=2$, ten if $\gdim=3$). Since a probability distribution concentrates within a small number of standard deviations of its mean, knowing $\mu(x)$ and $\Sigma(x)$ permits us to form an ellipsoid shaped a-priori estimate for the support of $\phi_x$. In other words, we can predict an ellipsoid outside of which $\phi_x$ will be (nearly) zero, \emph{without} computing $\phi_x$.

@@

\subsection{Overview of the method}
\label{sec:overview_intro}

>>>>

\subsection{Overview of the method}
Each impulse response $\impulseresponse_x$ may be interpreted as a scaled probability distribution because of the non-negative impulse response property. Let $\spatialvol(x) := \int_\Omega \impulseresponse_x(y) dy$ denote the scaling factor (the ``volume'' of $\impulseresponse_x$), let $\widehat{\impulseresponse}_x := \impulseresponse_x / \spatialvol(x)$ denote the normalized version of $\impulseresponse_x$, and let $\spatialmean(x)$ and $\spatialcov(x)$ denote the mean and covariance of $\widehat{\impulseresponse}_x$, respectively. In Section \ref{eq:mean_and_covariance_estimation} we will see that it is possible to compute $V(x)$, $\mu(x)$, and $\Sigma(x)$ for all $x \in \Omega$ simultaneously, via a procedure that involves applying $\Aop^T$ to a small number of polynomial functions (three functions if $\gdim=1$, six if $\gdim=2$, ten if $\gdim=3$). Since a probability distribution concentrates within a small number of standard deviations of its mean, knowing $\mu(x)$ and $\Sigma(x)$ permits us to form an ellipsoid shaped a-priori estimate for the support of $\phi_x$. In other words, we can predict an ellipsoid outside of which $\phi_x$ will be (nearly) zero, \emph{without} computing $\phi_x$.

@@

\subsection{Overview of the method (old)}
\label{sec:overview_intro}
